Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-10-16 ms.tex
tiny bit more on CV3 tests.

During the Cyrogenic Vacuum Test 3, the Integrated Science Instrument Module (ISIM) was placed in a vacuum chamber with a simulated telescope to illuminate the detectors in a similar way as during flight with an instrument called the Optical telescope element simulator (OSIM).
Of all ground-based tests discussed in this work, the point spread function most closely resembled the JWST flight point spread function.

@@

As with the spatial scanning mode on HST \citep[e.g.][]{mccullough2012spatialScan,deming13}, spreading the light of a source over many pixels can improve the precision of spectroscopy.
This is also accomplished by ground-based observatories by either de-focusing the telescope \citep{southworth2009defocusing} or by employing a beam-shaping diffuser \citep{stefansson2017diffusers}.
By spreading the light source over many pixels, the light curve becomes less sensitive to flat fielding or intra-pixel sensitivity errors with the jitter or seeing variations during an observation.
Similarly, NIRCam can employ a weak lens to defocus a star's light.
Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.
The hexagonal PSF is summed with circular aperture with a radius of 70 pixels.
The central peak may used to find a centroid of the star and center the circular aperture.

@@

A series of detector stability tests was performed using this +8 wave weak lens and 1.55 $\mu$m LED in a few different modes.

>>>>

During the Cyrogenic Vacuum Test 3, the Integrated Science Instrument Module (ISIM) was placed in a vacuum chamber with the Optical telescope element simulator (OSIM).
The ISIM has all the instruments with their internal optics and detectors but no telescope mirrors.
The OSIM simulates the PSF expected when a star or other point source illuminates the JWST instruments.
While other tests described in this work illuminated the science instrument detectors in different ways, the point spread function most closely resembled the JWST flight point spread function.

@@

As with the spatial scanning mode on HST \citep[e.g.][]{mccullough2012spatialScan,deming13}, spreading the light of a source over many pixels can improve the precision of spectroscopy.
This is also accomplished by ground-based observatories by either de-focusing the telescope \citep{southworth2009defocusing} or by employing a beam-shaping diffuser \citep{stefansson2017diffusers}.
By spreading the light source over many pixels, the light curve becomes less sensitive to flat fielding or intra-pixel sensitivity errors with telescope pointing jitter or seeing variations during an observation.
Similarly, NIRCam can employ a weak lens to defocus a star's light.
Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.
The hexagonal PSF is summed with circular aperture with a radius of 70 pixels.
The central peak may used to find a centroid of the star and center the circular aperture.

@@

A series of detector stability tests was performed using this +8 wave weak lens and 1.55 $\mu$m LED in a few different modes.
A time series of all possible modes is shown in Figure \ref{fig:CV3longTser}.
The full frame modes (FULL1 through FULLQ) used 2 samples of the ramp for integration times of 21.5 seconds whereas the subarrays were tuned to have a similar integration time (21.3 sec for 20 Groups of a 320$\times$320 subarray and 25.1 seconds for 6 groups of a 640$\times$640 subarray).
